What We Eval in the Shadows

### 2021-08-10 paper/main.tex
Add more info about side-effects

% TODO do assignments change types?

@@

\mypara{Discussion} In JavaScript assignments in \eval can happen in either
local scope or less often, when called through an alias, in the global scope. In
R, given the support for first-class environments, it can happen anywhere,
making it \eval more dangerous than it already is. However, the data suggest
that first, side-effects from \eval are not as widespread as in the case of
JavaScript,\footnote{\citep{ecoop11} shows that in the \emph{Interactive}
scenario, \eval in Javascript performs, store events can reach up to 40\% of the
events, and 7\% to 8\% of the \eval do side effects in the global scope. } and
that over half of them happen in a predictable environment.
% TODO connect the minimization group and side-effects

>>>>

@@

Out of the minimized expressions, it is \c{BLOCK}, \c{<-} and
\c{F(F(X)} that contribute to the vast majority of side effects. Concretely,
92\% of \c{BLOCK}, 87\% of \c{<-} and 15\% of \c{F(F(X))} expressions contain
side effects. In the case of \c{BLOCK}, most of the side effects happen in the
environment passed to \eval (which by default is the parent environment, \ie
the local or function in our classification). For \c{<-} it is 15\%, however,
that is only because of the \c{plyr::allocate\_column} which does the side
effect in the environment containing the data frame that is the target for the
newly allocated column. Without this call, \c{<-} is similarly predictable with
96\% of side effects in the passed environment. For \c{F(F(X))} minimization
for, it is less clear as 48\% of side effects happen in a different environment
to the one that was passed to \eval.

\mypara{Discussion} In JavaScript assignments in \eval can happen in either
local scope or less often, when called through an alias, in the global scope. In
R, given the support for first-class environments, it can happen anywhere,
making it \eval more dangerous than it already is. However, the data suggest
that first, side-effects from \eval are not as widespread as in the case of
JavaScript,\footnote{\citep{ecoop11} shows that in the \emph{Interactive}
scenario, \eval in Javascript performs, store events can reach up to 40\% of the
events, and 7\% to 8\% of the \eval do side effects in the global scope. } and
that over half of them happen in a predictable environment.
